{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-24 thesis/quicksand.tex
add line nrs to pp example program

\begin{figure}[t]
	\begin{center}
		\begin{tabular}{p{0.8\textwidth}}
			\begin{center}
			\begin{tabular}{ll}
				\multicolumn{2}{c}{Initially {\tt int count = \const{0}; mutex\_t m;}} \\
				\\
				{\bf Thread 1} & {\bf Thread 2} \\
				\hline
				\texttt{\hilight{darkorange}{mutex\_lock}(\&m);} & \texttt{atomic\_xadd(\&count, \const{1});} \\
				\texttt{count++;}                                & \texttt{\hilight{olivegreen}{yield}();} \\
				\texttt{\hilight{darkblue}{mutex\_unlock}(\&m);} & \texttt{atomic\_xadd(\&count, \const{1});} \\
				\texttt{assert(count >= \const{1});}      & \texttt{assert(count >= \const{2});} \\
			\end{tabular}
			\end{center}
			\\
			(a) Example program with synchronization API calls highlighted.
			\\
			\\
			\begin{center}
			\begin{tabular}{llc}
				{\bf Thread 1} & {\bf Thread 2} & {\bf Value of {\tt count}} \\
				\hline
				\texttt{\hilight{darkorange}{mutex\_lock}(\&m);} & & 0 \\
				\texttt{int tmp = count;} & & 0 \\
							& \texttt{atomic\_xadd(\&count, \const{1});} & 1 \\
							& \texttt{\hilight{olivegreen}{yield}();} & 1 \\
							& \texttt{atomic\_xadd(\&count, \const{1});} & 2 \\
				\texttt{count = tmp + 1;} & & 1 \\
							& \texttt{\hilight{assertfail}{assert(count >= 2);}} & 1 \\
				\texttt{\hilight{darkblue}{mutex\_unlock}(\&m);} & & 1 \\
				\texttt{assert(count >= \const{1});} & & 1 \\
			\end{tabular}
			\end{center}
			\\
			(b) Interleaving of (a) in which Thread 2's assertion fails,
			as the single increment of Thread 1 overwrites both those of Thread 2.
		\end{tabular}
	\end{center}
	\caption[Example bug requiring data-race preemption points to expose.]
	{Example bug requiring data-race preemption points to expose.
	Because the two threads use different modes of synchronization to protect their respective accesses to {\tt count},
	preempting on synchronization calls alone is insufficient to expose the bug.
	Rather, Thread 1 must be preempted between its non-atomic load and store of {\tt count}.
	}
	\label{fig:pps-example}
\end{figure}

>>>>

\begin{figure}[t]
	\begin{center}
		\begin{tabular}{p{0.8\textwidth}}
			\begin{center}
			\begin{tabular}{rlcrl}
				\multicolumn{5}{c}{Initially {\tt int count = \const{0}; mutex\_t m;}} \\
				\\
				& {\bf Thread 1} & & & {\bf Thread 2} \\
				\hline
				11 & \texttt{\hilight{darkorange}{mutex\_lock}(\&m);} & &
						21 & \texttt{atomic\_xadd(\&count, \const{1});} \\
				12 & \texttt{count++;}                                & &
						22 & \texttt{\hilight{olivegreen}{yield}();} \\
				13 & \texttt{\hilight{darkblue}{mutex\_unlock}(\&m);} & &
						23 & \texttt{atomic\_xadd(\&count, \const{1});} \\
				14 & \texttt{assert(count >= \const{1});}             & &
						24 & \texttt{assert(count >= \const{2});} \\
			\end{tabular}
			\end{center}
			\\
			(a) Example program with synchronization API calls highlighted.
			\\
			\\
			\begin{center}
			\begin{tabular}{llc}
				{\bf Thread 1} & {\bf Thread 2} & {\bf Value of {\tt count}} \\
				\hline
				\texttt{\hilight{darkorange}{mutex\_lock}(\&m);} & & 0 \\
				\texttt{int tmp = count;} & & 0 \\
							& \texttt{atomic\_xadd(\&count, \const{1});} & 1 \\
							& \texttt{\hilight{olivegreen}{yield}();} & 1 \\
							& \texttt{atomic\_xadd(\&count, \const{1});} & 2 \\
				\texttt{count = tmp + 1;} & & 1 \\
							& \texttt{\hilight{assertfail}{assert(count >= 2);}} & 1 \\
				\texttt{\hilight{darkblue}{mutex\_unlock}(\&m);} & & 1 \\
				\texttt{assert(count >= \const{1});} & & 1 \\
			\end{tabular}
			\end{center}
			\\
			(b) Interleaving of (a) in which Thread 2's assertion fails,
			as the single increment of Thread 1 overwrites both those of Thread 2.
		\end{tabular}
	\end{center}
	\caption[Example bug requiring data-race preemption points to expose.]
	{Example bug requiring data-race preemption points to expose.
	Because the two threads use different modes of synchronization to protect their respective accesses to {\tt count},
	preempting on synchronization calls alone is insufficient to expose the bug.
	Rather, Thread 1 must be preempted between its non-atomic load and store of {\tt count}.
	}
	\label{fig:pps-example}
\end{figure}
